### 2018-02-06 cover.tex
trying to get figures into online system

Please find the attached manuscript, entitled ``Haploid selection, sex ratio bias, and transitions between sex-determination systems'', which we submit to you for consideration for publication in \textit{PLoS Biology}.
\\

@@

Previous modelling studies include Muralidhar and Veller (2018, \textit{Nature Ecology and Evolution}), and van Doorn and Kirkpatrick (2007, \textit{Nature}; 2010, \textit{Genetics}), which have shown that a new sex determining allele can be favoured if it arises in linkage with sexually-antagonistic loci. 
One novel feature of our models is that we explicitly consider selection on loci that are very tightly linked to the ancestral sex-determining region.
Surprisingly, under various forms of selection, the unusual inheritance pattern of sex-linked loci can give rise to cases where the ancestral-X carries suboptimal alleles for females and/or the ancestral-Y carries female-beneficial alleles. 
This, in turn, can favour new sex-determining alleles that have weaker linkage with the loci under selection, which has not been predicted by previous theory. \\

It has been suggested that selection to balance the sex ratio is a dominant force driving transitions between sex-determining systems. 
Our models include haploid selection (meiotic drive or gametic competition), which can cause zygotic-sex ratios to become biased. 
In addition, haploid selection is usually sex-specific (occurring in either males or females only). 
Consequently, we find that haploid selection can cause transitions analogous to those caused by sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids. 
Unexpectedly, we do not find that selection to balance the sex ratio is overwhelming; transitions during which sex ratio biases increase or decrease are equally likely to evolve under a wide range of conditions. 
Furthermore, we find that looser linkage with the sex-determining region more often evolves when there is haploid selection, increasing the potential for lability in sex-determination. 
We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. \\

>>>>

Please find the attached manuscript, entitled ``Haploid selection, sex ratio bias, and transitions between sex-determination systems'', which we submit to you for consideration for publication in \textit{PLoS Biology}. Laurence Hurst and Nick Barton would be well qualified Academic Editors for this manuscript. 
\\

@@

Previous modelling studies, including Muralidhar and Veller (2018, \textit{Nature Ecology and Evolution}) and van Doorn and Kirkpatrick (2007, Nature; 2010, Genetics), have shown that a new sex determining allele can spread if it is more tightly linked to a sexually-antagonistic locus. Our work finds several surprising results in light of previous results. First, when the old sex determining allele is already tightly linked to a sexually-antagonistic locus, more loosely linked sex determining factors can invade under some circumstances, offering a new potential explanation for sex chromosome turnover. Second, when we include selection in the haploid phase (among gametes or gametophytes, including meiotic drive), entirely new predictions are generated for the spread of new sex determining factors.
In particular, selective differences between male and female diploids are no longer necessary;  conflicts between haploid and diploid selection can instead drive the invasion of new sex chromosomes. Interestingly, new sex chromosomes can spread under conditions where they balance the sex ratio but also under conditions where they lead to more skewed sex ratios. Indeed, transitions during which sex ratio biases increase or decrease are equally likely to evolve under a wide range of conditions. We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. \\

%Previous modelling studies include Muralidhar and Veller (2018, \textit{Nature Ecology and Evolution}), and van Doorn and Kirkpatrick (2007, \textit{Nature}; 2010, \textit{Genetics}), which have shown that a new sex determining allele can be favoured if it arises in linkage with sexually-antagonistic loci. 
%One novel feature of our models is that we explicitly consider selection on loci that are very tightly linked to the ancestral sex-determining region.
%Surprisingly, under various forms of selection, the unusual inheritance pattern of sex-linked loci can give rise to cases where the ancestral-X carries suboptimal alleles for females and/or the ancestral-Y carries female-beneficial alleles. 
%This, in turn, can favour new sex-determining alleles that have weaker linkage with the loci under selection, which has not been predicted by previous theory. \\

%It has been suggested that selection to balance the sex ratio is a dominant force driving transitions between sex-determining systems. 
%Our models include haploid selection (meiotic drive or gametic competition), which can cause zygotic-sex ratios to become biased. 
%In addition, haploid selection is usually sex-specific (occurring in either males or females only). 
%Consequently, we find that haploid selection can cause transitions analogous to those caused by sexually-antagonistic selection, eliminating the need for differences in selection between male and female diploids. 
%Unexpectedly, we do not find that selection to balance the sex ratio is overwhelming; transitions during which sex ratio biases increase or decrease are equally likely to evolve under a wide range of conditions. 
%Furthermore, we find that looser linkage with the sex-determining region more often evolves when there is haploid selection, increasing the potential for lability in sex-determination. 
%We conclude that haploid selection should be considered as a pivotal factor driving transitions between sex-determining systems. \\
